\documentclass[a4paper,12pt]{report}

\usepackage{color}

\setcounter{chapter}{1}

\begin{document}

\title{My First LaTeX Document}
\author{Md Ataullha}
\date{\today}
\maketitle

\pagenumbering{roman}
\tableofcontents
\newpage
\pagenumbering{arabic}

\addcontentsline{toc}{chapter}{Practical 1: Document Structure}
\chapter*{Practical 1: Document Structure}

\section{Introduction}This is the Introduction section.

\section{Methods} 
This is the Methods section.

\subsection{Stage 1}
\label{sec1}
This is the Stage 1 subsection and there is a label on it.
\subsubsection{Part 1}
This is another subsubsection under subsection.


\subsection{Stage 2}
This is anoter Stage 2 subsection.

\section{Results}
Here is the results section. Referring to section \ref{sec1} on page \pageref{sec1}.

\paragraph{First Paragraph}
This is a simple paragraph named First Paragraph. We used the pragraph command here.
\subparagraph{First Paragraph Sub Paragraph}
This is a subparagraph under the First paragraph.

\stepcounter{chapter} % if we do \stepcounter{chapter}{2} it will produce extra 2
\addcontentsline{toc}{chapter}{Practical 2: Typesetting Text}
\chapter*{Practical 2:Typesetting Text }

\section{Font Effects}
\textit{textit command for italitcs font effect.}\\
\textsl{textsl command for slanted font effect.}\\
\textsc{textsc command for smallcaps font effect.}\\
\textbf{textbf command for bold font effect.}\\
\texttt{texttt command for teletype font effect.}\\
\textsf{textsf command for sans serif font effect.}\\
\textrm{textrm command for roman font effect.}\\
\underline{underline command for underline font effect.}\\
\underline{\textbf{underline and textsc command for underline and bold font effect.}}\\

\section{Color Effects}
{\color{red}This is Red.}\\
{\color{green}This is Green.}\\
{\color{blue}This is Blue.}\\
{\color{cyan}This is Cyan.}\\
{\color{magenta}This is Magenta.}\\
{\color{yellow} This is Yellow.}\\
{\color{white}This is White.}\\

\section{Size Effects}
{\tiny tiny command for tiny font size.}\\
{\scriptsize scriptsize  command for scriptsize font size.}\\
{\small small command for small font size.}\\
{\normalsize normalsize command for normalsize font size.}\\
{\large large command for large font size.}\\
{\Large Large command for Large font size.}\\
{\LARGE LARGE  command for LARGE font size.}\\
{\huge huge command for huge font size}\\

\section{Lists}
A list and sub-list with enumerate only \\
\begin{enumerate}
\item First item.
\item Second item.
\begin{itemize}
\item A sub-item.
\item Another sub-item.
\end{itemize}
\item Third item.
\end{enumerate}

A list and sub-list \\
\begin{itemize}
\item First item.
\item Second item.
\begin{itemize}
\item A sub-item.
\item Another sub-item.
\end{itemize}
\item Third item.
\end{itemize}

A custom type list\\
\begin{itemize}
\item[-] First item.
\item[+] Second item.
\begin{itemize}
\item[ABC] A sub-item.
\item[DEF] Another sub-item.
\end{itemize}
\item[@] Third item.
\end{itemize}

\section{Comments}
Believe that life is worth living % Note comic irony in the very first sentence
, and your belief will help create the fact.

% This is a comment.

\vspace{12pt}
\vspace{12pt}
\vspace{12pt}
\vspace{12pt}
\vspace{12pt}
This is spacing.

\# \$ \% \^{} \& \_ \{ \} \~{}

\section{Spacing}
\vspace{12pt}
\vspace{12pt}
\vspace{12pt}

Item \#1A\textbackslash642 costs \$8 \& is sold at a \~{}10\% profit.

\end{document}